---
title: "Lab1"
author: "Tomohiro Justin Wada"
date: "2023-02-10"
output: pdf_document
---

```{r}
df = read.csv("Absenteeism_at_work.csv", sep = ";", header = TRUE)
attach(df)
```

# Question 1
```{r}
plot(Weight, Height, main = "Height VS Weight")
```
This is a scatter plot of Height vs Weight to depict if there is a correlation of height with weight. The plot does not depict of any significance to suggest anything.

# Question 2
```{r}
hist(Absenteeism.time.in.hours, xlab = "Absenteeism Time in Hours",
     main = "Historgram of Absenteeism Time in Hours")
```
This is a histogram representing absenteeism time in hours. It displays a large skew on the histogram not being too useful to decipher any useful information.

# Question 3
```{r}
hist(Age)
```
This is a histogram displaying the age and the total number of each age group. The histogram is useful to depict useful information regarding what is the main age demographic in this data.

# Quesiton 4
```{r}
library(dplyr)

df_summary <- df %>%
  group_by(Month.of.absence) %>%
  summarise(total_absenteeism_hours = sum(Absenteeism.time.in.hours))

barplot(df_summary$total_absenteeism_hours,
        names.arg = df_summary$Month.of.absence,
        xlab = "Months",
        ylab = "Total Absenteeism Hours",
        main = "Absent Hours of each Month")
```
This is a barplot displaying the total absenteeism hours for each month. This plot is useful to depict useful information regarding which month has the most hours absent.

# Question 5
```{r}
boxplot(Absenteeism.time.in.hours~Social.smoker, data=df, horizontal = T,
                                  col = c("purple", "blue"),
        xlab = "Absenteeism Time in Hours",
        ylab = "Social Smoker")

legend("topright", legend = c('Non-Smoker', 'Smoker'),
                    fil = c("purple", "blue"))
```
This is a boxplot displaying the absenteeism time in hours between smokers and non-smokers. This plot is not very useful to depict any information as the outlier points skews the boxplot.

# Question 6
```{r}
boxplot(Absenteeism.time.in.hours~Social.drinker, data=df, horizontal = T,
                                  col = c("purple", "blue"), 
        xlab = "Absenteeism Time in Hours",
        ylab = "Social Drinker")

legend("topright", legend = c('Non-Drinker', 'Drinker'),
                    fil = c("purple", "blue"))
```
This is a boxplot displaying the absenteeism time in hours between drinkers and non-drinkers. This plot is not very useful to depict any information as the outlier points skews the boxplot.





